DraftFunctions

### 2021-08-06 R/DraftFunctions.Rmd
#14 #35 #36

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
```

>>>>

```{r}
library(EcoFoG)
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
library(nngeo)
library(raster)
library(topoDistance)
library(BIOMASS)
```

```{r}
Paracou6_2016 <- Paracou6_2016 %>% 
  dplyr::select(-TreeFieldNum,-Project, -idVern, -CommercialSp, -CensusDate)

usethis::use_data(Paracou6_2016, overwrite = TRUE)
